### 2020-04-29 final_report/results.tex
finalise results of experiments 3-4

@@

\newpage

>>>>

In the fourth and final experiment, we exploit previously collected information
to produce surrogates with desirable properties for practical use. We
aim to create models that yield: (i)~the best regression performance regardless
of other features, (ii)~acceptable performance with the shortest mean
prediction time, or (iii)~acceptable performance with the smallest training set.
To this end, we trained 8~surrogates that are presented in~\cref{fig:reg-performance}
(more details are given in~\cref{tbl:exp4-detailed-results} in the Appendix).

@@

Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
experiments~2-3, we utilised the best-performing hyperparameter
assignments and training sets of varying sizes. In attempts to satisfy
goals~(i) and~(ii) within cross-validation setting, our best surrogate
achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\sigma=\num{8659251} \times$
with respect to the MC TBR evaluation baseline measured during run~1
(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
used the entire available set of~\num{500000} datapoints, in attempts to satisfy
goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\sigma=\num{1269777} \times$
using only a set of size~\num{10000}.

Overall we found that due to their excellent performance, boosted tree-based
approaches seem to be advantageous for fast surrogate modelling on relatively small training
sets (up to the order of~$10^4$). Conversely, while neural networks perform
poorly in such a setting, both their regression performance and prediction times
have proven superior on larger training sets (at least of the order of~$10^5$).
